---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Kai Zhen (11400302)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Matrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to its bullet points or use a new level 3 heading if you want.
-   Always render the R code for your solutions (`echo=TRUE`) and make
    sure to include the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown or Quarto document. Submit the files separately on moodle,
    **not** as a zip archive.
-   Submission format is HTML. Other formats will lead to a deduction of
    points.

## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  Start by initializing a new R project with git support, called
    `2025-exeRcise-sheet-3`. If you forgot how to do this, you can
    follow this
    [guide](https://malikaihle.github.io/Introduction-RStudio-Git-GitHub/rstudio_project.html).
b)  Commit the files generated by Rstudio.
c)  For all of the following tasks in this exercise sheet we ask you to
    always commit your changes after finishing each subtask e.g. create
    a commit after task *1d*, *1e* etc.

> Note: This applies only to answers that have text or code as their
> answer. If you complete tasks in a different order or forget to commit
> one, this is no problem. If you change your answers you can just
> create multiple commits to track the changes.

d)  Name 2 strengths and 2 weaknesses of git. (Don't forget to create a
    commit after this answer, see *1c*)
    
Strengths of git:

1. Extremely lightweight; fast performance for very low resource usage. 

2. Maintains comprehensive change history; keeps track of all changes to files
that are tracked with the ability to roll back changes.

Weaknesses of git:

1. Difficult to learn initially (use of command line, confusing
command names, getting used to git workflow, etc.).

2. Merge conflicts, especially with multiple team members, can become very
complicated and time consuming to resolve.
    
e)  Knit this exercise sheet. Some new files will automatically be
    generated when knitting the sheet e.g. the HTML page. Ignore these
    files, as we only want to track the source files themselves. You
    can, but don't need to create a `.gitignore` file. Just do not
    commit these files manually.

## Exercise 2: Putting your Repository on GitHub (3 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below:
    
https://github.com/kaixzhen/exeRcise-sheet-3
    
b)  Push your code to this new repository by copying and executing the
    snippet on github listed under
    `…or push an existing repository from the command line`.
c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.

## Exercise 3: Pixar Films (4 Points)

Download the `pixar_films` and `public_response` datasets from the
GitHub repository and track them in git.

Link:
<https://github.com/rfordatascience/tidytuesday/tree/main/data/2025/2025-03-11>

For small datasets like these adding them to git is not a problem.

```{r error=FALSE, message=FALSE}
library("tidyverse")
```

a)  Load the `pixar_films` dataset into R. Clean the dataset by removing
    films without a title. Inspect the variable `film_rating`. What are
    the possible values and what do they mean? Create a factor variable
    for the film rating. Why is this appropriate?

```{r}
df_pixar_films <- read_csv("data/pixar_films.csv")

df_pixar_films_clean <- df_pixar_films %>%
  filter(!is.na(film))

df_pixar_films_clean %>%
  print(n = 10)
```

According to the respective Data Dictionary on GitHub, the variable
`film_rating` represents the film rating based on the Motion Picture
Association (MPA) film rating system.
The possible values in this particular dataframe are:
G - General Audiences (All ages admitted)
PG - Parental Guidance Suggested (Some material may not be suitable for
children)

N/A values also appear, but these imply a missing value and don't have anything
to do with the rating system.

Creating a factor variable for the film rating:

```{r}
df_pixar_films_clean <- df_pixar_films_clean %>%
  mutate(
    film_rating_factor = factor(film_rating)
  )

df_pixar_films_clean %>%
  print(n = 10)
```

Factor variables represent categorical values and the MPA film rating system
inherently contains categories like G, PG, PG-13, etc. which makes it
appropriate in this case.

b)  Inspect the film titles manually. Which films form a film series? A
    film series can be identified by a common word in the titles of the
    films, often in conjunction with a number in the title,
    e.g. "Despicable Me" and "Despicable Me 2". Create a dataframe which
    displays a list of the different series with the titles of the films
    and how many films belong to the series. Output the dataframe.

Assigning each row a series:

```{r}
df_series <- df_pixar_films_clean %>%
  mutate(series = case_when(
    grepl("Toy Story", film) ~ "Toy Story",
    grepl("Monsters", film) ~ "Monsters",
    grepl("Finding", film) ~ "Finding",
    grepl("Incredibles", film) ~ "Incredibles",
    grepl("Cars", film) ~ "Cars",
    TRUE ~ "None"
  ))

df_series %>%
  print(n = 10)
```

Displaying series lists and number of films for each series:

```{r}
df_series <- df_series %>%
  group_by(series) %>%
  summarise(
    films = paste(film, collapse = ", "),
    number_films = n()
  ) %>%
  ungroup() %>%
  filter(series != "None") %>%
  print()
```

c)  Load the `public_response` dataframe into R. Convert the
    `cinema_score` variable into a factor while ensuring the factor
    levels are defined in ascending order, from the lowest to the
    highest score. Combine `public_response` with the `pixar_films`
    dataset using an appropriate merge variable.

Refactoring `cinema_score` variable:
    
```{r}
df_public_response <- read_csv("data/public_response.csv")

df_public_response <- df_public_response %>%
  mutate(
    cinema_score = fct_relevel(cinema_score, "A-", "A", "A+")
  )

df_public_response %>%
  print(n = 10)
```

Combining both datasets using `film` variable:

```{r}
df_pixar_films_with_reponse <- df_public_response %>%
  right_join(df_pixar_films_clean, by="film")

df_pixar_films_with_reponse %>%
  print(n = 10)
```

d)  Choose one of the variables representing the public response and
    create a bar plot for the films belonging to a series. Here are the
    details of the plot:

    -   The film series are represented on the x-axis.
    -   Your chosen public response variable is displayed on the y-axis.
    -   Each film in the series is represented as a separate bar. Bars
        are grouped by film under their respective series on the x-axis.
        Order the bars within a series according to the release date of
        the films.
    -   A title and axis labels for context.

    What do you notice when comparing the scores of the films in a
    series? Do you see any patterns?
    
Creating an appropriate dataframe:

```{r}
df_pixar_series_with_reponse <- df_pixar_films_with_reponse %>%
  mutate(
    series = case_when(
    grepl("Toy Story", film) ~ "Toy Story",
    grepl("Monsters", film) ~ "Monsters",
    grepl("Finding", film) ~ "Finding",
    grepl("Incredibles", film) ~ "Incredibles",
    grepl("Cars", film) ~ "Cars",
    TRUE ~ "None"),
    film = fct_reorder(film, release_date)
    ) %>%
  filter (series != "None")
  
```

Creating the bar plot:

```{r}
ggplot(
  data = df_pixar_series_with_reponse,
  mapping = aes(
    x = series,
    y = rotten_tomatoes,
    fill = film
  )
) +
  geom_bar(
    stat = "identity",
    position = "dodge"
  ) +
  labs(
    title = "Rotten Tomatoes Scores of Pixar Films by Series",
    x = "Film Series",
    y = "Rotten Tomatoes Score"
  )
```
When comparing the scores of the films in a series, sequels in general tend to
score worse than their predecessors.

## Exercise 4: Open Analysis (4 points)

This exercise is a bit more open-ended. You can choose any dataset from
[Our World in Data](https://ourworldindata.org/) and analyze it, while
determining the research question yourself.

a)  Go to <https://github.com/owid/owid-datasets/tree/master/datasets>
    and choose a dataset that interests you. You can have a look at
    <https://ourworldindata.org/> to gather some inspiration.
b)  Download the dataset and track it in git.
c)  Put the name / title of the dataset and a link to it below.

-   Dataset Name: Adult obesity by region - FAO (2017)
-   Link: <https://github.com/owid/owid-datasets/tree/master/datasets/Adult%20obesity%20by%20region%20-%20FAO%20(2017)>

d)  Come up with a (research) question you want to answer with the data
    and briefly explain why you believe this is an interesting question
    within one sentence. It should be a question that can be answered
    with the dataset and using R.
    
Research question: 

"Which regions in the world have the highest/lowest obesity rates and how do
they compare to the global obesity rate?"

This is an interesting question because it gives insight into how regional
differences in culture and lifestyle might affect obesity rates.

e)  Use R to answer your chosen question. Please limit your analysis to
    the functions and techniques we have covered so far in the course.
    You are **not expected** to use advanced statistical models or
    external packages which haven't been introduced.
f)  Create a meaningful plot / figure with the dataset. Make sure to
    provide a figure caption (via the chunk options / Rmarkdown) and
    correctly label the figure.

## Final Note

Make sure to push all your commits and changes to GitHub before
submitting the exercise sheet.
